LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2021-12-08 src/ms.tex
revert title, add margin icon for fig 1

\lw{} can be installed with pip or obtained from the GitHub repository \href{https://github.com/TeamLEGWORK/LEGWORK}{\faGithub}\footnote{\url{https://github.com/TeamLEGWORK/LEGWORK}}. All examples shown in this paper and code to reproduce the figures are available in the repository. Instructions for installation and basic usage are provided in the online documentation\footnote{\url{https://legwork.readthedocs.io/en/latest/}} which contain the most up-to-date instructions.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{static/package_overview.png}
    \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
    % \marginicon{\href{https://raw.githubusercontent.com/TeamLEGWORK/LEGWORK-paper/main/src/static/package_overview.png}{\color{lwColour}\faFileImage}}}
    \label{fig:package_overview}
\end{figure}

>>>>

\lw{} can be installed with pip or obtained from the GitHub repository \href{https://github.com/TeamLEGWORK/LEGWORK}{\color{\lwColour}\faGithub}\footnote{\url{https://github.com/TeamLEGWORK/LEGWORK}}. All examples shown in this paper and code to reproduce the figures are available in the repository. Instructions for installation and basic usage are provided in the online documentation\footnote{\url{https://legwork.readthedocs.io/en/latest/}} which contain the most up-to-date instructions.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{static/package_overview.png}
    \caption{Package structure of \lw{}. Each box represents a module and describes its function. The arrows indicate the inter-dependencies of the modules.}
    \marginicon{\href{https://raw.githubusercontent.com/TeamLEGWORK/LEGWORK-paper/main/src/static/package_overview.png}{\color{\lwColour}\faFileImage}}
    \label{fig:package_overview}
\end{figure}
